### 2016-08-26 RA-L/experiment.tex
Reorganized the paper

\begin{figure}
\begin{center}
	\includegraphics[width=.9\columnwidth]{SetUp.pdf}
\end{center}
\vspace{-1em}
\caption{\label{fig:setup}
Hardware platform:  table with 1.5$\times$1.2 m workspace, surrounded by eight remotely triggered 30W LED floodlights, with an overhead machine vision system.
}
\vspace{-1em}
\end{figure}

The walls of the hardware platform have almost infinite friction, due to a laser-cut, zigzag border and the three-legged design of the kilobots. When a kilobot is steered into the zigzag border, they pin themselves to the wall unless the global input directs them away from the wall.  This wall friction is sufficient to enable independent control of two kilobots, as shown in Fig.~\ref{fig:storyReal}.

To demonstrate covariance control $n$=100 robots were placed on the workspace and manually steered with a single light source, using friction with the boundary walls to vary the covariance from  -5000 to 10,000 pixel$^2$.  The resulting covariance is plotted in Fig.~\ref{fig:covExperiment}, along with snapshots of the swarm.

>>>>

\begin{figure}
\begin{center}
	\includegraphics[width=.9\columnwidth]{SetUp.pdf}
\end{center}
\vspace{-1em}
\caption{\label{fig:setup}
Hardware platform:  table with 1.5$\times$1.2 m workspace, surrounded by eight remotely triggered 30W LED floodlights, with an overhead machine vision system.
}
\vspace{-1em}
\end{figure}
\subsection{Hardware Experiment: Position Control of Two Robots}
The walls of the hardware platform have almost infinite friction, due to a laser-cut, zigzag border and the three-legged design of the kilobots. When a kilobot is steered into the zigzag border, they pin themselves to the wall unless the global input directs them away from the wall.  This wall friction is sufficient to enable independent control of two kilobots, as shown in Fig.~\ref{fig:storyReal}.

\subsection{Hardware Experiment: Position Control of n Robots}

\subsection{Hardware Experiment: Control of Covariance}
To demonstrate covariance control $n$=100 robots were placed on the workspace and manually steered with a single light source, using friction with the boundary walls to vary the covariance from  -5000 to 10,000 pixel$^2$.  The resulting covariance is plotted in Fig.~\ref{fig:covExperiment}, along with snapshots of the swarm.

### 2016-08-26 RA-L/intro.tex
Reorganized the paper

\section{Introduction}\label{sec:Intro}
Micro- and nano-robots can be manufactured in large numbers, see recent examples in~\citet{Donald2013}, \citet{Ghosh2009}, \citet{kim2015imparting}, \citet{qiu2015magnetic}, or \citet{martel2014computer}.
Someday large swarms of robots will be remotely guided
 1)  ex vivo to assemble structures in parallel and 
2) through the human body, to cure disease, heal tissue, and prevent infection. %Both tasks are high   as described in \citet{munoz2014review} \citet{sitti2015biomedical} . 
 For each application, large numbers of micro robots are required  to deliver sufficient payloads, but the small size of these robots makes it difficult to perform onboard computation.  Instead, these robots are often controlled by a global, broadcast signal. 
These applications require control techniques that can reliably exploit large populations despite high under-actuation.

>>>>

\section{Introduction}\label{sec:Intro}
Micro- and nano-robots can be manufactured in large numbers, see recent examples in~\citet{Chowdhury2015}, \citet{martel2014computer}, \citet{kim2015imparting}, \citet{Donald2013}, \citet{Ghosh2009}, or \citet{qiu2015magnetic}.
Someday large swarms of robots will be remotely guided
 1)  ex vivo to assemble structures in parallel and 
2) through the human body, to cure disease, heal tissue, and prevent infection. %Both tasks are high   as described in \citet{munoz2014review} \citet{sitti2015biomedical} . 
 For each application, large numbers of micro robots are required  to deliver sufficient payloads, but the small size of these robots makes it difficult to perform onboard computation.  Instead, these robots are often controlled by a global, broadcast signal. 
These applications require control techniques that can reliably exploit large populations despite high under-actuation.

### 2016-08-26 RA-L/simulation.tex
Reorganized the paper

Algorithms \ref{alg:PosControl2Robots}, \ref{alg:XControl}, \ref{alg:YControl}, were implemented in Mathematica using point robots (radius = $0$).  Fig.~\ref{fig:shapeControlMathematica1}  shows  this algorithm for two configurations. 
Robot initial positions are shown by a crosshair, and final positions by a circled crosshair.  Dashed lines show the shortest route if robots could be controlled independently.  The path given by  Alg.\ \ref{alg:PosControl2Robots} is shown with solid arrows.
Each row has five snapshots taken every quarter second. For the sake of brevity axis-aligned moves were replaced with oblique moves that combine two moves simultaneously. 
 $\Delta r_x$ is adjusted to $\Delta e_x$ in the second snapshot at $t = 0.25$. 
 The following frames  adjust $\Delta r_y$ to $\Delta e_y$. 
 $\Delta r_y$ is corrected by $t = 0.75$. 
 Finally, the algorithm moves the robots to their corresponding destinations.

In the worse case, adjusting both $\Delta r_x$ and $\Delta r_y$ requires two iterations.   Two iterations of Alg. \ref{alg:XControl} are only required if $|\Delta e_x - \Delta s_x|>L$. 
Similarly,  two iterations of Alg. \ref{alg:YControl} are only required if $|\Delta e_y - \Delta s_y|>L$.

@@

\subsection{Efficient Control of Covariance}
A set of simulations were conducted to demonstrate the importance of boundary friction.  These simulations use  the 2D physics engine Box2D, by \citet{catto2010box2d}.
 144 disc-shaped robots were controlled by an open-loop control input as illustrated in Fig. \ref{fig:SimCovarianceFuncFrictionOpenLoop}.  All robots had  the same initial conditions, but in four tests the boundary friction was $F_f = \{0,1/3 F, 2/3F, F\}$.
 Without friction, covariance has minimal variation.  As friction increases, the covariance can be manipulated to greater degrees.

>>>>

Algorithms \ref{alg:PosControl2Robots}, \ref{alg:XControl}, %\ref{alg:YControl}, 
were implemented in Mathematica using point robots (radius = $0$).  Fig.~\ref{fig:shapeControlMathematica1}  shows  this algorithm for two configurations. 
Robot initial positions are shown by a crosshair, and final positions by a circled crosshair.  Dashed lines show the shortest route if robots could be controlled independently.  The path given by  Alg.\ \ref{alg:PosControl2Robots} is shown with solid arrows.
Each row has five snapshots taken every quarter second. For the sake of brevity axis-aligned moves were replaced with oblique moves that combine two moves simultaneously. 
 $\Delta r_x$ is adjusted to $\Delta e_x$ in the second snapshot at $t = 0.25$. 
 The following frames  adjust $\Delta r_y$ to $\Delta e_y$. 
 $\Delta r_y$ is corrected by $t = 0.75$. 
 Finally, the algorithm moves the robots to their corresponding destinations.

In the worse case, adjusting both $\Delta r_x$ and $\Delta r_y$ requires two iterations.   Two iterations of Alg. \ref{alg:XControl} are only required if $|\Delta e_x - \Delta s_x|>L$. 
Similarly,  two iterations %of Alg. \ref{alg:YControl} 
are only required if $|\Delta e_y - \Delta s_y|>L$.

@@

\subsection{Efficient Control of Covariance}
%A set of simulations were conducted to demonstrate the importance of boundary friction.  
Random disturbances impair the performance of Alg. \ref{alg:PosControl2Robots} and Alg. \ref{alg:PosControlNRobots}. Still, we are able to control covariance of the swarm. This section demonstrates simulations of controlling covariance of the swarm.
These simulations use  the 2D physics engine Box2D, by \citet{catto2010box2d}.
 144 disc-shaped robots were controlled by an open-loop control input as illustrated in Fig. \ref{fig:SimCovarianceFuncFrictionOpenLoop}.  All robots had  the same initial conditions, but in four tests the boundary friction was $F_f = \{0,1/3 F, 2/3F, F\}$.
 Without friction, covariance has minimal variation.  As friction increases, the covariance can be manipulated to greater degrees.

### 2016-08-26 RA-L/theory.tex
applied some review comments
Reorganized the paper

\subsection{Controlling Covariance: Fluid Settling In a Tank}\label{subsec:FluidInTank}
One method to control a swarm's shape in a bounded workspace is to simply push in a given direction until the swarm conforms to the boundary.
\paragraph{Square workplace}
This section examines the mean, variance,  covariance and correlation of a very large swarm of robots as they move inside a square workplace under the influence of gravity pointing in the direction $\beta$. The swarm is large, but the robots are small in comparison, and together cover an area of constant volume $A$. Under a global input such as gravity, they flow like water, moving to a side of the workplace and forming a polygonal shape, as shown in Fig.~\ref{fig:SquareFill}.

@@

\subsection{Friction with Boundary Wall}\label{subsec:WallFriction}
Global inputs move a swarm uniformly.  
Controlling covariance requires breaking this uniform symmetry.  A swarm inside an axis-aligned rectangular workspace can reduce variance normal to a wall by simply pushing the swarm into the boundary. Directly controlling covariance by pushing the swarm into a boundary requires changes to the boundary.  An obstacle in the lower-right corner is enough to generate positive covariance.  Generating both positive and negative covariance requires additional obstacles.  Requiring special obstacle configuration also makes covariance control dependent on the local environment. 
  Instead of pushing our robots directly into a wall, this paper examines an oblique approach, by using boundaries that generate friction with the robots.  These frictional forces are  sufficient to break the symmetry caused by uniform inputs.  Robots touching a wall have a negative friction force that opposes movement along the boundary.  This  causes robots along the boundary to slow down compared to robots in free-space.

@@

\subsection{Position Control of $2$ Robots Using Wall Friction}\label{sec:PostionControl2Robots}
\begin{figure*}
\centering
\renewcommand{\figwid}{0.4\columnwidth}
{\begin{overpic}[width =\figwid]{one_1.jpg}\put(45,75){$t$ = 0 s}
\end{overpic}
\begin{overpic}[width =\figwid]{one_2.jpg}\put(45,75){$t$ = 0.25 s}
\end{overpic}
\begin{overpic}[width =\figwid]{one_3.jpg}\put(45,75){$t$  = 0.5 s}
\end{overpic}
\begin{overpic}[width =\figwid]{one_4.jpg}\put(45,75){$t$  = 0.75 s}
\end{overpic}
\begin{overpic}[width =\figwid]{one_5.jpg}\put(45,75){$t$  = 1 s}
\end{overpic}}\\
%{\begin{overpic}[width =\figwid]{two_1.jpg}\put(45,75){$t$  = 0 s}
%\end{overpic}
%\begin{overpic}[width =\figwid]{two_2.jpg}\put(45,75){$t$  = 0.25 s}
%\end{overpic}
%\begin{overpic}[width =\figwid]{two_3.jpg}\put(45,75){$t$  = 0.5 s}
%\end{overpic}
%\begin{overpic}[width =\figwid]{two_4.jpg}\put(45,75){$t$  = 0.75 s}
%\end{overpic}
%\begin{overpic}[width =\figwid]{two_5.jpg}\put(45,75){$t$  = 1 s}
%\end{overpic}}\\
\vspace{.5em}
{\begin{overpic}[width =\figwid]{S3_1.jpg}\put(45,75){$t$ = 0 s}
\end{overpic}
\begin{overpic}[width =\figwid]{S3_2.jpg}\put(45,75){$t$ = 0.25 s}
\end{overpic}
\begin{overpic}[width =\figwid]{S3_3.jpg}\put(45,75){$t$  = 0.5 s}
\end{overpic}
\begin{overpic}[width =\figwid]{S3_4.jpg}\put(45,75){$t$  = 0.75 s}
\end{overpic}
\begin{overpic}[width =\figwid]{S3_5.jpg}\put(45,75){$t$  = 1 s}
\end{overpic}}
\vspace{-1em}
\caption{\label{fig:shapeControlMathematica1}{Frames from an implementation of Alg.\ \ref{alg:PosControl2Robots}: two robot positioning using walls with infinite friction. The algorithm only requires friction along the bottom and left walls.
Robot initial positions are shown by a crosshair, and final positions by a circled crosshair.  Dashed lines show the shortest route if robots could be controlled independently.  The path given by  Alg.\ \ref{alg:PosControl2Robots} is shown with solid arrows.
The bottom row shows an extreme case where the robots must switch position.
}
%\vspace{-2em}
}
\end{figure*}

@@

Our algorithm solves the positioning problem in two steps: 
First, $|\Delta r_x - \Delta e_x |$ is reduced to zero while  $\Delta r_y$ is kept constant in Alg.~\ref{alg:XControl}. 
Second $|\Delta r_y - \Delta e_y |$ is reduced to zero while  $\Delta r_x$ is kept constant in Alg.~\ref{alg:YControl}.

Step (i): Fixing $\Delta r_x$
\label{theory:step1}
\begin{enumerate}
\item
If $\Delta e_x$ is negative, the robots will be commanded to move toward the left wall and halt $\epsilon$ distance from the left wall.
If $\Delta e_x \ge 0$, the robots will be commanded to move toward the right wall and halt $\epsilon$ distance from the right wall. The epsilon distance prevents the robots from experiencing friction along the vertical wall.
\item  let $y_{\min} = \min_i r_{iy}$, i.e., $y_{\min}$ be the minimum height of the two robots. Move both robots downward  $y_{\min}$ such that one of the robots touches the bottom wall and hence friction force will prevent this robot from moving left or right.
\item friction force holds the lower robot in place while the upper robot may move right and left freely to change $\Delta r_x $ to $\Delta e_x$.
\item  If after the free move of the upper robot $\Delta r_x$ is not $\Delta e_x$, Step (i) will be repeated.  No more than two iterations of step (i) are required.
\end{enumerate}

Step (ii): Fixing $\Delta r_y$
Now that $\Delta r_x$ is corrected, $\Delta r_y$ must be corrected:
\begin{enumerate}
\item 
If $\Delta e_y$ is negative, the robots will be commanded to move toward the top wall and halt $\epsilon$ distance from the top wall.
If $\Delta e_y \ge 0$, the robots will be commanded to move toward the bottom wall and halt $\epsilon$ distance from the bottom wall. The epsilon distance prevents the robots from experiencing friction along the horizontal wall.
\item  let $x_{\min} = \min_i r_{ix}$, i.e., $x_{\min}$ be the minimum distance of the two robots from the origin along the $x$-axis. Move both robots to the left $x_{\min}$ such that one of the robots  touches the left wall and hence friction force will prevent this robot from moving up or down.
\item  friction force holds the left robot in place while the right robot may move up or down freely to change $\Delta r_y $  to $\Delta e_y$.
\item  If after the free move of the right robot $\Delta r_y$ is not $\Delta e_y$, Step (ii) will be repeated.  No more than two iterations of step (ii) are required.
\end{enumerate}
Once $\Delta r_x$ and $\Delta r_y$ are set to $\Delta e_x$ and $\Delta e_y$, a straight-line global input moves both robots from $r_1$ and $r_2$ to $e_1$ and $e_2$.

@@

\begin{algorithm}
\caption{GenerateDesired$y$-spacing($s_1,s_2,e_1,e_2,L$)}\label{alg:YControl}
\begin{algorithmic}[1]
\Require Knowledge of starting $(s_1,s_2)$ and ending $(e_1,e_2)$ positions of  two robots. 
$(0,0)$ is bottom corner, $s_1$ is rightmost robot, 
 $L$ is length of the walls. Current robot positions are $(r_1,r_2)$.
\Ensure   $ r_{1x} - r_{2x}  \equiv s_{1x} - s_{2x} $   %$\Delta y(t) \equiv \Delta y(0)$ 
\State $ \Delta s_y  \gets s_{1y} - s_{2y} $
\State $ \Delta e_y \gets e_{1y} - e_{2y} $
\State $ r_1 \gets s_1$, $ r_2 \gets s_2$
\If {$\Delta e_y < 0 $ }
\State $ m \gets ( L-\max( r_{1y},r_{2y}) ,0)   $ \Comment{Move to top wall}
\Else 
\State  $ m \gets ( -\min( r_{1y},r_{2y}),0 )    $ \Comment{Move to bottom wall}
\EndIf
\State $m  \gets  m + (0, -\min( r_{1x},r_{2x} ))$ \Comment{Move to left}
\State $ r_1 \gets r_1+m$, $ r_2 \gets r_2+m$ \Comment{Apply move}
\If {$\Delta e_y - (r_{1y} - r_{2y} ) > 0 $}
\State $ m \gets (\min(|\Delta e_y - \Delta s_y |, L- r_{1y}), 0)$  \Comment{Move top}
\Else
\State $ m \gets (-\min(|\Delta e_y - \Delta s_y |, r_{1y}), 0)$\Comment{Move bottom}
\EndIf 
\State $m  \gets  m + (0, \epsilon)$ \Comment{Move right}
\State $ r_1 \gets r_1+m$, $ r_2 \gets r_2+m$ \Comment{Apply move}
\State $\Delta r_y = r_{1y} - r_{2y}$
\If {$\Delta r_y \equiv \Delta e_y$} 
\State   $ m \gets (e_{1x}-r_{1x}, e_{1y}-r_{1y})$
\State $ r_1 \gets r_1+m$, $ r_2 \gets r_2+m$ \Comment{Apply move}
\State  \Return $(r_1,r_2)$
\Else   
\State \Return GenerateDesired$y$-spacing($r_1,r_2,e_1,e_2,L$)
\EndIf
\end{algorithmic}
\end{algorithm}

\subsection{Position Control of $n$ Robots Using Wall Friction}\label{sec:PostionControlnRobots}
Alg. \ref{alg:PosControl2Robots}  can be extended to control the position of $n$ robots using wall friction under several constraints. The solution described here is an iterative procedure with $n$ loops. The $k$th loop moves the $k$th robot from a \emph{staging zone} to the desired position in a \emph{build zone}. At the end the $k$th loop, robots 1 through $k$ are in their desired final configuration in the build zone, and robots $k+1$ to $n$ are in the staging zone. See Fig.~\ref{fig:construction2d} for a schematic of the build and staging zones.

>>>>

\subsection{Using Boundaries: Fluid Settling In a Tank}\label{subsec:FluidInTank}
One method to control a swarm's shape in a bounded workspace is to simply push in a given direction until the swarm conforms to the boundary.
\paragraph{Square workplace}
This section examines the mean, variance,  covariance and correlation of a very large swarm of robots as they move inside a square workplace under the influence of gravity pointing in the direction $\beta$. The swarm is large, but the robots are small in comparison, and together occupy a constant area $A$. Under a global input such as gravity, they flow like water, moving to a side of the workplace and forming a polygonal shape, as shown in Fig.~\ref{fig:SquareFill}.

@@

\subsection{Using Boundaries: Friction and Boundary Layers}\label{subsec:WallFriction}
Global inputs move a swarm uniformly.  
Controlling covariance requires breaking this uniform symmetry.  A swarm inside an axis-aligned rectangular workspace can reduce variance normal to a wall by simply pushing the swarm into the boundary. Directly controlling covariance by pushing the swarm into a boundary requires changes to the boundary.  An obstacle in the lower-right corner is enough to generate positive covariance.  Generating both positive and negative covariance requires additional obstacles.  Requiring special obstacle configuration also makes covariance control dependent on the local environment. 
  Instead of pushing our robots directly into a wall, this paper examines an oblique approach, by using boundaries that generate friction with the robots.  These frictional forces are  sufficient to break the symmetry caused by uniform inputs.  Robots touching a wall have a negative friction force that opposes movement along the boundary.  This  causes robots along the boundary to slow down compared to robots in free-space.

@@

\section{Algorithms}\label{sec:algorithms}
\subsection{Position Control of $2$ Robots Using Wall Friction}\label{sec:PostionControl2Robots}
\begin{figure*}
\centering
\renewcommand{\figwid}{0.4\columnwidth}
{\begin{overpic}[width =\figwid]{one_1.jpg}\put(45,75){$t$ = 0 s}
\end{overpic}
\begin{overpic}[width =\figwid]{one_2.jpg}\put(45,75){$t$ = 0.25 s}
\end{overpic}
\begin{overpic}[width =\figwid]{one_3.jpg}\put(45,75){$t$  = 0.5 s}
\end{overpic}
\begin{overpic}[width =\figwid]{one_4.jpg}\put(45,75){$t$  = 0.75 s}
\end{overpic}
\begin{overpic}[width =\figwid]{one_5.jpg}\put(45,75){$t$  = 1 s}
\end{overpic}}\\
%{\begin{overpic}[width =\figwid]{two_1.jpg}\put(45,75){$t$  = 0 s}
%\end{overpic}
%\begin{overpic}[width =\figwid]{two_2.jpg}\put(45,75){$t$  = 0.25 s}
%\end{overpic}
%\begin{overpic}[width =\figwid]{two_3.jpg}\put(45,75){$t$  = 0.5 s}
%\end{overpic}
%\begin{overpic}[width =\figwid]{two_4.jpg}\put(45,75){$t$  = 0.75 s}
%\end{overpic}
%\begin{overpic}[width =\figwid]{two_5.jpg}\put(45,75){$t$  = 1 s}
%\end{overpic}}\\
\vspace{.5em}
{\begin{overpic}[width =\figwid]{S3_1.jpg}\put(45,75){$t$ = 0 s}
\end{overpic}
\begin{overpic}[width =\figwid]{S3_2.jpg}\put(45,75){$t$ = 0.25 s}
\end{overpic}
\begin{overpic}[width =\figwid]{S3_3.jpg}\put(45,75){$t$  = 0.5 s}
\end{overpic}
\begin{overpic}[width =\figwid]{S3_4.jpg}\put(45,75){$t$  = 0.75 s}
\end{overpic}
\begin{overpic}[width =\figwid]{S3_5.jpg}\put(45,75){$t$  = 1 s}
\end{overpic}}
\vspace{-1em}
\caption{\label{fig:shapeControlMathematica1}{Frames from an implementation of Alg.\ \ref{alg:PosControl2Robots}: two robot positioning using walls with infinite friction. The algorithm only requires friction along the bottom and left walls.
Robot initial positions are shown by a crosshair, and final positions by a circled crosshair.  Dashed lines show the shortest route if robots could be controlled independently.  The path given by  Alg.\ \ref{alg:PosControl2Robots} is shown with solid arrows.
The bottom row shows an extreme case where the robots must switch position.
}
%\vspace{-2em}
}
\end{figure*}

@@

Our algorithm solves the positioning problem in two steps: 
First, $|\Delta r_x - \Delta e_x |$ is reduced to zero while  $\Delta r_y$ is kept constant in Alg.~\ref{alg:XControl}. 
Second $|\Delta r_y - \Delta e_y |$ is reduced to zero while  $\Delta r_x$ is kept constant.% in Alg.~\ref{alg:YControl}.

%Step (i): Fixing $\Delta r_x$
%\label{theory:step1}
%\begin{enumerate}
%\item
%If $\Delta e_x$ is negative, the robots will be commanded to move toward the left wall and halt $\epsilon$ distance from the left wall.
%If $\Delta e_x \ge 0$, the robots will be commanded to move toward the right wall and halt $\epsilon$ distance from the right wall. The epsilon distance prevents the robots from experiencing friction along the vertical wall.
%\item  let $y_{\min} = \min_i r_{iy}$, i.e., $y_{\min}$ be the minimum height of the two robots. Move both robots downward  $y_{\min}$ such that one of the robots touches the bottom wall and hence friction force will prevent this robot from moving left or right.
%\item friction force holds the lower robot in place while the upper robot may move right and left freely to change $\Delta r_x $ to $\Delta e_x$.
%\item  If after the free move of the upper robot $\Delta r_x$ is not $\Delta e_x$, Step (i) will be repeated.  No more than two iterations of step (i) are required.
%\end{enumerate}
%
%Step (ii): Fixing $\Delta r_y$
%Now that $\Delta r_x$ is corrected, $\Delta r_y$ must be corrected:
%\begin{enumerate}
%\item 
%If $\Delta e_y$ is negative, the robots will be commanded to move toward the top wall and halt $\epsilon$ distance from the top wall.
%If $\Delta e_y \ge 0$, the robots will be commanded to move toward the bottom wall and halt $\epsilon$ distance from the bottom wall. The epsilon distance prevents the robots from experiencing friction along the horizontal wall.
%\item  let $x_{\min} = \min_i r_{ix}$, i.e., $x_{\min}$ be the minimum distance of the two robots from the origin along the $x$-axis. Move both robots to the left $x_{\min}$ such that one of the robots  touches the left wall and hence friction force will prevent this robot from moving up or down.
%\item  friction force holds the left robot in place while the right robot may move up or down freely to change $\Delta r_y $  to $\Delta e_y$.
%\item  If after the free move of the right robot $\Delta r_y$ is not $\Delta e_y$, Step (ii) will be repeated.  No more than two iterations of step (ii) are required.
%\end{enumerate}
%Once $\Delta r_x$ and $\Delta r_y$ are set to $\Delta e_x$ and $\Delta e_y$, a straight-line global input moves both robots from $r_1$ and $r_2$ to $e_1$ and $e_2$. 
%

@@

%\begin{algorithm}
%\caption{GenerateDesired$y$-spacing($s_1,s_2,e_1,e_2,L$)}\label{alg:YControl}
%\begin{algorithmic}[1]
%\Require Knowledge of starting $(s_1,s_2)$ and ending $(e_1,e_2)$ positions of  two robots. 
%$(0,0)$ is bottom corner, $s_1$ is rightmost robot, 
% $L$ is length of the walls. Current robot positions are $(r_1,r_2)$.
%\Ensure   $ r_{1x} - r_{2x}  \equiv s_{1x} - s_{2x} $   %$\Delta y(t) \equiv \Delta y(0)$ 
%\State $ \Delta s_y  \gets s_{1y} - s_{2y} $
%\State $ \Delta e_y \gets e_{1y} - e_{2y} $
%\State $ r_1 \gets s_1$, $ r_2 \gets s_2$
%\If {$\Delta e_y < 0 $ }
%\State $ m \gets ( L-\max( r_{1y},r_{2y}) ,0)   $ \Comment{Move to top wall}
%\Else 
%\State  $ m \gets ( -\min( r_{1y},r_{2y}),0 )    $ \Comment{Move to bottom wall}
%\EndIf
%\State $m  \gets  m + (0, -\min( r_{1x},r_{2x} ))$ \Comment{Move to left}
%\State $ r_1 \gets r_1+m$, $ r_2 \gets r_2+m$ \Comment{Apply move}
%\If {$\Delta e_y - (r_{1y} - r_{2y} ) > 0 $}
%\State $ m \gets (\min(|\Delta e_y - \Delta s_y |, L- r_{1y}), 0)$  \Comment{Move top}
%\Else
%\State $ m \gets (-\min(|\Delta e_y - \Delta s_y |, r_{1y}), 0)$\Comment{Move bottom}
%\EndIf 
%\State $m  \gets  m + (0, \epsilon)$ \Comment{Move right}
%\State $ r_1 \gets r_1+m$, $ r_2 \gets r_2+m$ \Comment{Apply move}
%\State $\Delta r_y = r_{1y} - r_{2y}$
%\If {$\Delta r_y \equiv \Delta e_y$} 
%\State   $ m \gets (e_{1x}-r_{1x}, e_{1y}-r_{1y})$
%\State $ r_1 \gets r_1+m$, $ r_2 \gets r_2+m$ \Comment{Apply move}
%\State  \Return $(r_1,r_2)$
%\Else   
%\State \Return GenerateDesired$y$-spacing($r_1,r_2,e_1,e_2,L$)
%\EndIf
%\end{algorithmic}
%\end{algorithm}

\subsection{Position Control of $n$ Robots Using Wall Friction}\label{sec:PostionControlnRobots}
Alg. \ref{alg:PosControl2Robots}  can be extended to control the position of $n$ robots using wall friction under several constraints. The solution described here is an iterative procedure with $n$ loops. The $k$th loop moves the $k$th robot from a \emph{staging zone} to the desired position in a \emph{build zone}. All robots move according to the global input, but due to wall friction, at the end the $k$th loop, robots 1 through $k$ are in their desired final configuration in the build zone, and robots $k+1$ to $n$ are in the staging zone. See Fig.~\ref{fig:construction2d} for a schematic of the build and staging zones.
